{\bf Landslide: Systematic Dynamic Race Detection in Kernel-space}

### 2012-05-10 defence/defence.tex
minor update
write focusing slides

\begin{frame}{The Kernel as One Program} % slide: the kernel is too big to test all at once
	% say: it's also important to understand the kernel's internals instead of just viewing it as one ``black box''
	\begin{center}
	\includegraphics[width=\textwidth]{pebbles.png}
	\end{center}
	% now that we see these internal interfaces, how do we apply systematic testing to it?
\end{frame}
\begin{frame}{The Kernel as One Program} % slide: the kernel is too big to test all at once
	\begin{itemize}
		\item ``Everything interleaves with everything else''?
		\item What is a ``bug'', anyway?\related{Baumann '09}
	\end{itemize}
	% Say: "we don't want to have to explore every possible interaction between each of these components"
\end{frame}

@@

\begin{frame}{Decision Trace}
	% FIXME make the stack trace coloured
	\includegraphics[width=\textwidth]{found_a_bug.png}
\end{frame}

@@

		Definite bugs
		\begin{itemize}
			\item Kernel panics / assertion failures
			\item Use-after-free
			\item Deadlock
		\end{itemize}
		Probable bugs
		\begin{itemize}
			\item Infinite loop
			\begin{itemize}
				\item Use structure of execution tree to judge progress.
			\end{itemize}
		\end{itemize}
		\column{0.25\textwidth}
		\includegraphics[width=\textwidth]{livelock.png}
	\end{columns}
\end{frame}
% slide: other_prob: decide on mutex_lock as opposed to everywhere, but...
% slide: manual shaping - have *user* specify what to focus on (automating intuition)
\begin{frame}{Limiting Decision Points}
\end{frame}
% slide: exciting teaser "i think this is not too far off!"
\begin{frame}{Teaser}
\end{frame}

@@

>>>>

\begin{frame}{The Kernel as One Program} % slide: the kernel is too big to test all at once
	% say: it's also important to understand the kernel's internals instead of just viewing it as one ``black box''
	\begin{center}
	\includegraphics[width=\textwidth]{pebbles.png}
	\end{center}
	% now that we see these internal interfaces, how do we apply systematic testing to it?
\end{frame}
\begin{frame}{The Kernel as One Program} % slide: the kernel is too big to test all at once
	``Everything interleaves with everything else''?
	\begin{itemize}
		% Say: "we don't want to have to explore every possible interaction between each of these components"
		\item Impractical to explore resulting state spaces
	\end{itemize}
	\linegap

	What is a ``bug'', anyway?\related{Baumann '09}
\end{frame}

@@

\begin{frame}{Decision Trace}
	% FIXME make the stack trace coloured
	\includegraphics[width=\textwidth]{found_a_bug.png}
	% Say: So landslide had to explore 5 different interleavings to find the bug. But this was a pretty simple test case, and 
\end{frame}

@@

		Definite bugs
		\begin{itemize}
			\item Kernel panics / assertion failures
			\item Use-after-free
			\item Deadlock
		\end{itemize}
		Probable bugs
		\begin{itemize}
			\item Infinite loop
			\begin{itemize}
				\item Use structure of execution tree to judge progress.
			\end{itemize}
		\end{itemize}
		\column{0.25\textwidth}
		\includegraphics[width=\textwidth]{livelock.png}
	\end{columns}
\end{frame}
% slide: other_prob: decide on mutex_lock as opposed to everywhere, but...
% slide: manual shaping - have *user* specify what to focus on (automating intuition)
\begin{frame}{Focusing the Search Space}
	Recommended decision points: \texttt{mutex\_lock()} and \texttt{mutex\_unlock()}
	\linegap

	{\bf Problem:} Kernel uses mutexes {\em everywhere}.
	\begin{itemize}
		\item Good: \texttt{exit()} calls \texttt{mutex\_lock()}
		\item Bad: \texttt{exit()} calls \texttt{destroy\_address\_space()} calls \texttt{mutex\_lock()}
	\end{itemize}
	\linegap
	{\bf Solution:} User specifies what modules of the kernel to pay attention to.
	\begin{itemize}
		\item \texttt{within\_function exit}
		\item \texttt{without\_function destroy\_address\_space}
	\end{itemize}
\end{frame}
% slide: exciting teaser "i think this is not too far off!"
\begin{frame}{Teaser: (Semi-)Automated Search Focusing}
	Searching for bugs given a stack trace
	\begin{itemize}
		\item User knows {\em where} the bug is, but not {\em what}.
		\item Testing framework can use stack trace to conduct a more focused search.
	\end{itemize}
\end{frame}

@@

\breakslide{Evaluating Landslide}
